\textit{Supporting Information for}: Geometric models reveal behavioral and neural signatures of transforming naturalistic experiences into episodic memories

### 2020-09-05 paper/supporting_information.tex
updated Fig S3 caption

\begin{figure}[]
\centering
\includegraphics[width=1\textwidth]{figs/feature_value}
\caption{\small \textbf{Feature importance analysis.} \textbf{A.} Contributions of each feature type to the structure of the episode topic proportions matrix. The bar heights reflect the correlation between the episode topic proportions matrix computed using all features with an episode topic proportions matrix computed using all features except the indicated feature.  (Lower bars reflect features that contribute more substantially to the episode's temporal structure.) \textbf{B.} Which features are preserved during recall?  The bar heights reflect the (average) across-participant correlations between the episode and recall trajectories.  Error bars denote bootstrap-estimated standard error of the mean.  \textbf{C.} Feature correlation matrix.  Each entry displays the correlation between episode topic trajectories created using only the indicated (row/column) features.}
\label{fig:feature-importance}
\end{figure}

>>>>

\begin{figure}[]
\centering
\includegraphics[width=1\textwidth]{figs/feature_value}
\caption{\small \textbf{Feature importance analysis.} \textbf{A.} Contributions of each feature type to the structure of the episode topic proportions matrix. The bar heights reflect the correlation between the proximal temporal structure (see \textit{Methods}) of the episode topic proportions matrix computed using all features, and that of an episode topic proportions matrix computed using all features except the indicated feature.  Lower bars reflect features that contribute more substantially to the episode's temporal structure. \textbf{B.} Which features are preserved during recall?  The bar heights reflect the (average) across-participant correlations between the proximal temporal structure of episode and recall topic proportions matrices constructed in the absence of the given feature.  Error bars denote standard error of the mean.  \textbf{C.} Feature correlation matrix.  Each entry displays the correlation between episode topic portions matrices created using only the indicated (row/column) features.}
\label{fig:feature-importance}
\end{figure}
